---
title: "CoEDL Summer School 2019 :: Advanced Statistics for Linguists (coedlstatzr)"
author: "Martin Schweinberger <www.martinschweinberger.de>"
date: "contact: m.schweinberger@uq.edu.au"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## CoEDL Summer School 2019 - Advanced Statistics for Linguists (coedlstatzr)

Before we start, download the zip-file "AdvancedStatzForLinguists", unzip wherever you please and open it (all you will ever need - for this work shop - is in that folder)!

You can automatically download the zipped folder from <https://martinschweinberger.de/docs/materials/AdvancedStatzForLinguists.zip>.

All code and more elaborate explainations of what we will cover is available at the LADAL website (Language Technology and Data Analysis Laboratory; <https://slcladal.github.io/index.html>) hosted by the *School of Languages and Culters* of The University of Queensland, Australia (UQ)

## About this Course

What will we cover?

- Simple linear regression
- Fixed-effects regression (linear|logistic)
- Mixed-effects regression (linear|logistic|quasi-poisson)
- Tree-based models (Conditional Inference Trees|Random Forests|Boruta)

Aims

- Understand these methods
- Use these methods
- Being aware of their advantages|disadvantages|problems|issues

## About this Course

What this course is **NOT**

- This is not an introduction to statistics 

- This is not an intro to R

What will we **NOT** cover?

- Basic concepts (probability, significance, etc.) 

- Yes, everything ww will do will be done in R but we cannot go into how R works

- Technical trouble shooting (cry for help and the assitants will come and assits in crying)

- The mathematical underpinning of the models (unless absolutely neccessary)


## Timeline

**Session 1 (Thursday 10:00 to 11:30)**

- Introduction and set up

- Simple linear and multiple fixed-effects regression

**Session 2 (Thursday 9:00 to 10:30)**

- More multiple fixed-effects regression and start with mixed-effects regression

**Session 3 (Friday 11:00 to 12:30)**

- Mixed-effects regression

**Session 4 (Friday 11:00 to 12:30)**

- Tree-based models

- Wrap-up and goodbye

## Why R?

- Free open-source software
- Fuly-fledged programming environment
- Enables and enhances full reproducibility/replicability of your research (enables Best Practices)
- Can be used fro data science/management/processing/visualization/analytics/presentation
- Massive and friendly support-infrastructure 

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

